Supplementary Appendix: Trends in the contribution of major causes of death to the black-white life expectancy gap by US state. A retrospective study of all deaths between 1969 and 2013

### 2018-05-09 Manuscript/Appendix-agestd-mort-rates.Rmd
update plots

```{r plot_LE_trends_males, echo=F, fig.height=10, fig.width=13}
LE_trend_plot_males +
  geom_hline(aes(yintercept = 0), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 10), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 15), lwd = 0.5, col = "grey", alpha = 0.5)

@@

```{r plot_LE_trends_females, echo=F, fig.height=10, fig.width=13}
LE_trend_plot_females +
  geom_hline(aes(yintercept = -5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 0), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 10), lwd = 0.5, col = "grey", alpha = 0.5)

>>>>

```{r plot_LE_trends_males, echo=F, fig.height=10, fig.width=13}
le.gap.men <- LE_trend_plot_males +
  geom_hline(aes(yintercept = 0), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 10), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 15), lwd = 0.5, col = "grey", alpha = 0.5) + 
  ggtitle("A) Black-white life expectancy gap in men")

@@

```{r plot_LE_trends_females, echo=F, fig.height=10, fig.width=13}
le.gap.women <- LE_trend_plot_females +
  geom_hline(aes(yintercept = -5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 0), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 10), lwd = 0.5, col = "grey", alpha = 0.5) +
  ggtitle("B) Black-white life expectancy gap in women")

ggsave(filename = "../Plots/figure1a.jpeg", plot = le.gap.men, device = "jpeg", width = 12, height = 10, units = "in")
ggsave(filename = "../Plots/figure1b.jpeg", plot = le.gap.women, device = "jpeg", width = 12, height = 10, units = "in")
```
